%-------------------------------------------

% Resume in Latex
% Author : Charlie Scott

%----------PREAMBLE----------
\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage{xparse}
\usepackage{xstring}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{mdframed}

% Page style settings
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

%----------CUSTOM COMMANDS----------

% Bullet points
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Formatting sections, headings, items
% Section
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Name
\NewDocumentCommand{\Introduction}{ m m m m }{
    \def\Name{#1}
    \def\Email{#2}
    \def\LinkedinUser{#3}
    \def\GithubUser{#4}
    \begin{center}
        \textbf{\Huge \Name} \\ \vspace{1pt}
        \href{mailto:\Email}{\underline{\Email}} $|$
        \href{https://linkedin.com/in/\LinkedinUser}{\underline{linkedin.com/in/\LinkedinUser}} $|$
        \href{https://github.com/\GithubUser}{\underline{github.com/\GithubUser}}
    \end{center}
}

% Heading
\NewDocumentCommand{\Heading}{ m o m m }{
    \def\Company{#1}
    \def\CompanyURL{#2}
    \def\Timespan{#3}
    \def\Details{#4}
    \item
    \IfValueTF{\CompanyURL}{%
        {\bfseries\href{\CompanyURL}{\Company}}% If URL is provided
    }{%
        {\bfseries\Company}% If URL is not provided
    }\hfill{\small \Timespan}\\
    {\itshape\small \Details\/}
}

% SubHeading
\NewDocumentCommand{\SubHeading}{ m }{
    \def\Project{#1}
    \item
    {\bfseries \Project}
    \vspace{4pt} % Space below subheading
}

% Item
\newcommand{\Item}[1]{
  \item\small{
    \parbox[t]{500pt}{\raggedright#1}
  }
}

% Lists
% Heading List
\newenvironment{HeadingList}{
  \begin{mdframed}[
    topline=false,
    bottomline=false,
    rightline=false,
    leftline=false,
    linecolor=gray,
    linewidth=0pt,
    leftmargin=0pt,
    innerleftmargin=0pt,
    innertopmargin=0pt,
    innerbottommargin=0pt,
    innerrightmargin=0pt,
    skipabove=\parsep,
    skipbelow=\parsep,
  ]
  \begin{itemize}[leftmargin=0pt, label={}]
}{
  \end{itemize}
  \end{mdframed}
}

% SubHeading List
\newenvironment{SubHeadingList}{
  \begin{mdframed}[
    leftline=true,
    linecolor=gray,
    linewidth=.5pt,
    leftmargin=8pt,
    innerleftmargin=8pt,
  ]
  \begin{itemize}[leftmargin=0pt, label={}]
}{
  \end{itemize}
  \end{mdframed}
}

% ItemList
\newenvironment{ItemList}{
  \begin{itemize}[itemsep=4pt, topsep=-3pt, partopsep=0pt, parsep=0pt, leftmargin=20pt, label=\raisebox{0.4ex}{\scalebox{0.5}{\textbullet}}]
}{\end{itemize}}

%-------------------------------------------

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------NAME-----------

\Introduction{Charlie Scott}{charliejscott@outlook.com}{charliejscott}{cscott20}

%-----------EXPERIENCE-----------

\section{Experience}
    \begin{HeadingList}
        \Heading{Echo AI}[https://www.echoai.com]{June 2021--Present}{Software Engineer $|$ New York, NY}
            \begin{SubHeadingList}

                \SubHeading{Conversation Intelligence Analytics}
                \begin{ItemList}
                    \Item{Led development of a core feature for a new product, generating over \$1m in revenue in under 200 days.}
                    \Item{Allows users to simultaneously analyze AI insights generated for hundreds of thousands of conversations between their customer service agents and customers.}
                    \Item{Developed continuous improvement plan to incrementally improve performance of product over time to meet future customer needs.}
                    \Item{Directly worked with customers to identify needs, and created product roadmaps to implement feature requests over time.}
                    \Item{Onboarded multiple engineers onto new platform to allow for faster development.}
                \end{ItemList}

                \SubHeading{Conversation Intelligence Performance Management}
                \begin{ItemList}
                    \Item{Led development of core feature that uses AI to create admin dashboards to provide team performance insights.}
                    \Item{New feature allows leaders to easily identify teamwide areas of both improvement, and achievement. Designed reusable heatmap grid components to create a user friendly visual for complex datasets.}
                    \Item{Wrote technical documents, led design discussions, and coordinated with organization leaders to future-proof the product, allowed future product developments to be easily integrated into the app.}
                \end{ItemList}

                \SubHeading{Reinforced Learning Platform}
                \begin{ItemList}
                    \Item{Owner of new platform that allows administrators and agents to provide feedback on AI generated insights.}
                    \Item{Developed algorithms to intelligently select areas in need of human feedback.}
                    \Item{Designed database schema, API endpoints, and GUI to support feedback on variety of existing database models.}
                    \Item{Project directly addressed customer concerns around AI inaccuracies, and directly led to increased accuracy through model fine tuning using data collected.}
                \end{ItemList}

            \end{SubHeadingList}


        \Heading{Epsilon}[https://www.epsilon.com/us]{Sept 2020--June 2021}{Software Engineer $|$ San Francisco, CA}
            \begin{SubHeadingList}

                \SubHeading{Safe Database Interaction Tool}
                \begin{ItemList}
                    \Item{Developed full stack web apps which allowed users to safely and easily modify production databases through GUI.}
                    \Item{Automated labor intensive developer tasks related to monitoring of company cloud platform performance.}
                    \Item{Proactively maintained cloud infrastructure to ensure smooth and efficient operations.}
                \end{ItemList}

            \end{SubHeadingList}

        \Heading{Cigna}[https://www.cigna.com]{June 2019--Aug 2019}{Intern $|$ Santa Monica, CA}
            \begin{SubHeadingList}

                \SubHeading{Data and Research Task Automation Project}
                \begin{ItemList}
                    \Item{Independently contacted and worked with product managers to understand business needs. Led to starting new project to automate online data collection that was previously done manually.}
                    \Item{Integrated this new application with existing manual data collection pipelines to ease transition.}
                    \Item{Developed tools to speed existing process of manual data collection efforts by upwards of 30\% per employee.}
                \end{ItemList}

        \end{SubHeadingList}
    \end{HeadingList}

%-----------EDUCATION-----------

\section{Education}
    \begin{HeadingList}
        \Heading{BS Mathematics, Computer Science}{Aug 2017--June 2020}{California Polytechnic University}
        \begin{ItemList}
            \Item{Graduated early with honors, including Dean's List recognition and an Academic Excellence Award of Honor. Received the Department of Mathematics Glassco Scholarship for academic excellence.}
            \Item{Collaborated with the Dean to design a specialized Computer Science concentration tailored to the Mathematics focus program.}
        \end{ItemList}
    \end{HeadingList}

\end{document}

%-------------------------------------------