%-------------------------
% Resume in Latex
% Author : Charles Scott
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------NAME-----------
\begin{center}
    \textbf{\Huge Charles J. Scott} \\ \vspace{1pt}
    \small 805-368-9038 $|$ \href{mailto:x@x.com}{\underline{charliejscott@outlook.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/charliejscott}} $|$
    \href{https://github.com/...}{\underline{github.com/cscott20}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{June 2021 -- Present}
      {Pathlight}{San Francisco, CA}
      \resumeItemListStart
      \resumeItem{Full stack product software engineer using Django, React, Javascript, Python, SCSS.}
\resumeItem{Initiating and leading new feature development to increase user engagement.}
\resumeItem{Designing, building, and testing new features from ideation to deployment.}
\resumeItem{Responding to customer feature requests, investigating and fixing time sensitive bugs\\throughout the product.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Sept. 2020 -- June 2021}
      {Epsilon Data Management}{Westlake Villiage, CA}
      \resumeItemListStart
        \resumeItem{Building full stack RESTful web service applications from ideation to launch.}
        \resumeItem{Developing automated tools to increase workflow efficiency and remotely\\monitor cluster health.}
        \resumeItem{Supporting and maintaining company cloud platform.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
   \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Work Force Management Scheduling, Project Co Lead}}{Pathlight}
          \resumeItemListStart
            \resumeItem{Co lead of major paywalled feature add to product involving multiple engineers.}
            \resumeItem{Responsible for writing technical design documents, as well as making major feature\\decisions along with design and product teams.}
            \resumeItem{Created the most well tested feature on the application, with both front end\\and back end unit \& functional tests tests.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Cookies, Project Lead}}{Pathlight}
          \resumeItemListStart
            \resumeItem{Project lead, started as an idea for eng team hackathon, saw development through to launch.}
            \resumeItem{New feature to increase product engagement, allowing employees to send recognition to peers.}
            \resumeItem{Incremental scope increase including user facing dashboard, and tying cookies to compensation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{New Customer Implementation, Project Lead}}{Pathlight}
          \resumeItemListStart
            \resumeItem{Ingesting customer data into Pathlight through open source tap apis, and Amazon Connect.}
            \resumeItem{Communicating across multiple teams to relay goals and implementation progress to customer.}
            \resumeItem{Improving tap reliability.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Triage Engineer}}{Pathlight}
          \resumeItemListStart
            \resumeItem{Serving as primary engineer in charge of responding to urgent customer reported\\and site-wide bugs.}
            \resumeItem{Prioritization delegation of multiple simultaneous incoming bugs.}
            \resumeItem{Ensuring bug resolution timelines are met and relayed to customers.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Configs As A Service, Project Lead}}{Epsilon}
          \resumeItemListStart
            \resumeItem{Built REST APIs, as well as interactive front end webpages with about 20 endpoints.}
            \resumeItem{Full stack development using Spring Boot and production SQL DBs.}
            \resumeItem{Replaced existing service with application to automate job processes\\and increase maintainability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Polytechnic State University}{Aug. 2017 -- June 2020}
      {B.S. Mathematics, Concentration Computer Science $|$ San Luis Obispo, CA}{}
      \resumeItemListStart
        \resumeItem{Early graduate, Dean’s List recipient, Academic Excellence Award of Honor recipient,\\Department of Mathematics Glassco Scholarship recipient.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
